---
title: "03_descriptive_statistics"
---

```{r}
#install.packages(c("bit64", "readr", "data.table", "psych", "dplyr", "tidyr", "reshape2", "lubridate", "forecast", "astsa", "zoo", "nowcasting", "TSstudio", "pastecs", "grid", "gridExtra"))

library(readr)
library(data.table)
library(psych)
library(dplyr)
library(tidyr)
library(reshape2)
library(lubridate)
library(forecast)
library(astsa)
library(zoo)
library(nowcasting)
library(TSstudio)
library(ggplot2)
library(pastecs)
library(readxl)
library(gridExtra)
library(grid)
```

#Descriptive Statistics

```{r group by campsite}
fullData <- fread("fullData.csv")
camp <- fullData[grepl("Overnight", fullData[["UseType"]]), ] 
rm(fullData)

camp$dateDiff <- as.Date(as.character(camp$StartDate), format="%Y-%m-%d") - as.Date(as.character(camp$OrderDate), format="%Y-%m-%d")
camp$dateDiff <- as.numeric(camp$dateDiff)+1
camp$lengthStay <- as.Date(as.character(camp$EndDate), format="%Y-%m-%d") - as.Date(as.character(camp$StartDate), format="%Y-%m-%d")

camp$lengthStay <- as.numeric(camp$lengthStay) 
camp2 <- camp[camp$dateDiff>=0 ,]
camp2 <- camp2[camp2$EndDate>0 ,]

#delete non-camp grouns identified by Will
camp2 <- camp2 %>%
  subset(Park != "BROOKS CAMP (Search under Permits - Katmai NP)" & Park != "CAMP ROUND MEADOW" & Park != "JUNIPER LAKE STOCK CORRAL" & Park != "Kenai Fjords National Park Cabins" & Park != "MANZANITA LAKE CAMPING CABINS" & Park != "Priest Rock Cabin" & Park != "SUMMIT LAKE STOCK CORRAL")%>%
  select(HistoricalReservationID, RegionDescription, ParentLocation, Park, ProductID, FacilityID, UseFee, TotalPaid, StartDate, EndDate, OrderDate, NumberOfPeople, dateDiff, lengthStay)

rm(camp)
```

```{r}
a <- NULL
list <- unique(camp2$Park)[1:30]

startTime <- Sys.time()
cat("startTime is:", startTime)

for (name in list){
  temp <- camp2[which(camp2$Park==name),]
  temp <- temp[,cbind(.SD, date=(as.Date(StartDate)):as.Date(EndDate)),by="HistoricalReservationID"]
  temp$date <- as.Date(temp$date, origin = "1970-01-01")
  temp <- temp %>%
    group_by(date) %>%
    mutate(totalNumberOfPeople = sum(NumberOfPeople)) %>%
    mutate(avgNumberOfPeople = mean(NumberOfPeople)) %>%
    mutate(occupancy = length(unique(ProductID))) %>%
    mutate(aggPaid = sum(TotalPaid)) %>%
    mutate(avgPaid = mean(TotalPaid)) %>%
    mutate(avgfee = mean(UseFee/lengthStay)) %>%
    mutate(avglengthStay = mean(lengthStay)) %>%
    mutate(minlengthStay = min(lengthStay)) %>%
    mutate(maxlengthStay = max(lengthStay)) %>%
    mutate(avgdateDiff = mean(dateDiff)) %>%
    mutate(mindateDiff = min(dateDiff)) %>%
    mutate(maxdateDiff = max(dateDiff))
a <- bind_rows(a, temp)
}

fwrite(a, file = "descriptive1.csv")
endTime <-  Sys.time()
runningTime <- endTime - startTime
print (startTime)
print (endTime)
print (runningTime)
cat ("LBJ final name is:", name)

list <- unique(camp2$Park)[31:60]
a <- NULL

startTime <- Sys.time()
cat("startTime is:", startTime)

for (name in list){
  temp <- camp2[which(camp2$Park==name),]
  temp <- temp[,cbind(.SD, date=(as.Date(StartDate)):as.Date(EndDate)),by="HistoricalReservationID"]
  temp$date <- as.Date(temp$date, origin = "1970-01-01")
  temp <- temp %>%
    group_by(date) %>%
    mutate(totalNumberOfPeople = sum(NumberOfPeople)) %>%
    mutate(avgNumberOfPeople = mean(NumberOfPeople)) %>%
    mutate(occupancy = length(unique(ProductID))) %>%
    mutate(aggPaid = sum(TotalPaid)) %>%
    mutate(avgPaid = mean(TotalPaid)) %>%
    mutate(avgfee = mean(UseFee/lengthStay)) %>%
    mutate(avglengthStay = mean(lengthStay)) %>%
    mutate(minlengthStay = min(lengthStay)) %>%
    mutate(maxlengthStay = max(lengthStay)) %>%
    mutate(avgdateDiff = mean(dateDiff)) %>%
    mutate(mindateDiff = min(dateDiff)) %>%
    mutate(maxdateDiff = max(dateDiff))
a <- bind_rows(a, temp)
}

fwrite(a, file = "descriptive2.csv")
endTime <-  Sys.time()
runningTime <- endTime - startTime
print (startTime)
print (endTime)
print (runningTime)
cat ("LBJ final name is:", name)

list <- unique(camp2$Park)[61:108]
a <- NULL

startTime <- Sys.time()
cat("startTime is:", startTime)

for (name in list){
  temp <- camp2[which(camp2$Park==name),]
  temp <- temp[,cbind(.SD, date=(as.Date(StartDate)):as.Date(EndDate)),by="HistoricalReservationID"]
  temp$date <- as.Date(temp$date, origin = "1970-01-01")
  temp <- temp %>%
    group_by(date) %>%
    mutate(totalNumberOfPeople = sum(NumberOfPeople)) %>%
    mutate(avgNumberOfPeople = mean(NumberOfPeople)) %>%
    mutate(occupancy = length(unique(ProductID))) %>%
    mutate(aggPaid = sum(TotalPaid)) %>%
    mutate(avgPaid = mean(TotalPaid)) %>%
    mutate(avgfee = mean(UseFee/lengthStay)) %>%
    mutate(avglengthStay = mean(lengthStay)) %>%
    mutate(minlengthStay = min(lengthStay)) %>%
    mutate(maxlengthStay = max(lengthStay)) %>%
    mutate(avgdateDiff = mean(dateDiff)) %>%
    mutate(mindateDiff = min(dateDiff)) %>%
    mutate(maxdateDiff = max(dateDiff))
a <- bind_rows(a, temp)
}

fwrite(a, file = "descriptive3.csv")
endTime <-  Sys.time()
runningTime <- endTime - startTime
print (startTime)
print (endTime)
print (runningTime)
cat ("LBJ final name is:", name)

rm(temp)
b <- fread("descriptive1.csv")
c <- fread("descriptive2.csv")

b$date <- as.Date(b$date, format = "%Y-%m-%d")
c$date <- as.Date(c$date, format = "%Y-%m-%d")

full <- bind_rows(a,b,c)

rm(a,b,c)
fwrite(full, file="descriptive_f.csv")
```

```{r column movig function}
moveMe <- function(data, tomove, where = "last", ba = NULL) {
  temp <- setdiff(names(data), tomove)
  x <- switch(
    where,
    first = data[c(tomove, temp)],
    last = data[c(temp, tomove)],
    before = {
      if (is.null(ba)) stop("must specify ba column")
      if (length(ba) > 1) stop("ba must be a single character string")
      data[append(temp, values = tomove, after = (match(ba, temp)-1))]
    },
    after = {
      if (is.null(ba)) stop("must specify ba column")
      if (length(ba) > 1) stop("ba must be a single character string")
      data[append(temp, values = tomove, after = (match(ba, temp)))]
    })
  x
}
```

```{r read in data}
setwd("C:/Users/sup97/Box Sync/RIDB Article/DataAnalysis")
initialData <- fread("descriptive_f.csv")

initialData <- initialData %>%
  subset(Park != "BROOKS CAMP (Search under Permits - Katmai NP)" & Park != "CAMP ROUND MEADOW" & Park != "JUNIPER LAKE STOCK CORRAL" & Park != "Kenai Fjords National Park Cabins" & Park != "MANZANITA LAKE CAMPING CABINS" & Park != "Priest Rock Cabin" & Park != "SUMMIT LAKE STOCK CORRAL") %>%
  distinct(Park, date, occupancy, .keep_all = TRUE)

#give unique id to each park
data <- transform(initialData,id=as.numeric(factor(initialData$Park)))
list <- unique(data$id) #108 id's created

min(as.Date(data$date, format="%Y-%m-%d")) #"2007-01-10"
max(as.Date(data$date, format="%Y-%m-%d")) #"2018-12-02"
```

```{r match with mother Park}
parklist <- read_excel("C:/Users/soyou/Box Sync/RIDB Article/list of parks_WLR_2.0.xlsx")
colnames(parklist)[colnames(parklist)=="Our Data"] <- "Campground"
colnames(parklist)[colnames(parklist)=="# Sites"] <- "numOfSites"
colnames(parklist)[colnames(parklist)=="# Sites on Rec.gov"] <- "recGovNumOfSites"
colnames(parklist)[colnames(parklist)=="Booking Min"] <- "bookingMin"
colnames(parklist)[colnames(parklist)=="Booking Max"] <- "bookingMax"
colnames(parklist)[colnames(parklist)=="X__1"] <- "Release"

parklist <- subset(parklist, Campground != "BROOKS CAMP (Search under Permits - Katmai NP)" & Park != "CAMP ROUND MEADOW" & Campground != "JUNIPER LAKE STOCK CORRAL" & Campground != "Kenai Fjords National Park Cabins" & Campground != "MANZANITA LAKE CAMPING CABINS" & Campground != "Priest Rock Cabin" & Campground != "SUMMIT LAKE STOCK CORRAL")

parklist$Park[parklist$Park=="Lassen Volanic"] <- "Lassen Volcanic" ##there was typo...
parklist$Park[parklist$Campground=="Grey Cliffs Campground"] <- "Great Basin" ##Grey Cliffs Campground is in Great Basin

##Match Campground to Park
colnames(data)[colnames(data)=="Park"] <- "Campground"
data <- dplyr::left_join(data, parklist, by="Campground")

#agg <- aggregate(data=data, Campground ~ Park, function(x) length(unique(x)))
#agg <- left_join(agg, parklist, by="Park")
#agg <- agg %>%
#  select(Park, Campground.x, numOfSites, recGovNumOfSites) %>%
#  group_by(Park) %>%
#  mutate(numOfSites = sum(as.numeric(numOfSites))) %>%
#  mutate(recGovNumOfSites=sum(as.numeric(recGovNumOfSites))) %>%
#  distinct()

#colnames(agg)[colnames(agg)=="Campground.x"] <- "Campground"
#kable(agg, "latex", booktabs = T)
```

```{r clean up data}
##Reorder data columns
#data$HistoricalReservationID <- NULL
data$ParentLocation <- NULL
#data$ProductID <- NULL
data$numOfSites <- as.numeric(data$numOfSites)
data$recGovNumOfSites <- as.numeric(data$recGovNumOfSites)
data <- data %>%
  moveMe(c("id", "Park", "Campground", "date", "occupancy", "avglengthStay", "avgfee"), "first") %>%
  moveMe(c("StartDate", "EndDate", "OrderDate", "HistoricalReservationID", "RegionDescription", "ProductID", "FacilityID", "NumberOfPeople", "UseFee", "TotalPaid"), "last")

##"INDIAN COVE CAMPGROUND"  "BUTTE LAKE STOCK CORRAL" thsese two do not have number of sites
data$numOfSites[data$Campground=="BUTTE LAKE STOCK CORRAL"] = 1
data$recGovNumOfSites[data$Campground=="BUTTE LAKE STOCK CORRAL"] = 1
data$Park[data$Campground=="BUTTE LAKE STOCK CORRAL"] = "Lassen Volcanic"
data$numOfSites[data$Campground=="INDIAN COVE CAMPGROUND"] = 101

##Change occupancy to percentage
data <- data %>%
  select(id, Park, Campground, date, occupancy, avglengthStay, avgfee, avgdateDiff, totalNumberOfPeople, avgNumberOfPeople, aggPaid, avgPaid, numOfSites, recGovNumOfSites) %>%
  group_by(Campground) %>%
  group_by(date) %>%
  mutate(occupancy = occupancy/recGovNumOfSites)

fwrite(data, "final_data.csv")
```

```{r}
#Without group sites - 77 campgrounds, 29 parks - still with more than 100 average fee
NGdata <- data[!grepl("GROUP", data$Campground),]
NGdata <- NGdata[!grepl("Group", NGdata$Campground),]

#Without those with greater than 100 USD average daily fee to avoid bias
NFdata <- data[data$avgfee<=100,]
summary(NFdata)
```

```{r Descriptive statistics}
#We want occupancy, average number of people, average fee, length of stay, how far in average people book in advance at the PARK level for description
descriptive <- NFdata %>%
  select(Park, date, occupancy, avgNumberOfPeople, avgfee, avglengthStay, avgdateDiff) %>%
  group_by(Park) %>%
  group_by(date) %>%
    mutate(avgNumberOfPeople = sum(avgNumberOfPeople)) %>%
    mutate(occupancy = mean(occupancy)) %>%
    mutate(avgfee = mean(avgfee)) %>%
    mutate(avglengthStay = mean(avglengthStay)) %>%
    mutate(avgdateDiff = mean(avgdateDiff)) %>% 
    distinct(Park, date, .keep_all = TRUE)

group <- descriptive %>%
  group_by(Park) %>%
  summarise(
    avgNumberOfPeople = mean(avgNumberOfPeople), 
    occupancy = mean(occupancy),
    avgfee = mean(avgfee),
    avglengthStay = mean(avglengthStay),
    avgdateDiff = mean(avgdateDiff)
    )
```

```{r descriptive plots}
library(ggplot2)
library(scales)
library(tidyverse)

ANP <- group %>%
  mutate(Park = fct_reorder(Park, avgNumberOfPeople)) %>%
  ggplot(aes(y = avgNumberOfPeople, x = Park)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_flip()  + 
  labs(x = "", y = "Average Number of People") +
  theme_classic() +
  theme(legend.position="NA")

OCC <- group %>%
  mutate(Park = fct_reorder(Park, occupancy)) %>%
  ggplot(aes(y = occupancy, x = Park)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_flip()  + 
  labs(x = "", y = "Average Occupancy") +
  theme_classic() +
  theme(legend.position="NA")

AVF <- group %>%
  mutate(Park = fct_reorder(Park, avgfee)) %>%
  ggplot(aes(y = avgfee, x = Park)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_flip()  + 
  labs(x = "", y = "Average Daily Fee") +
  theme_classic() +
  theme(legend.position="NA")

ALS <- group %>%
  mutate(Park = fct_reorder(Park, avglengthStay)) %>%
  ggplot(aes(y = avglengthStay, x = Park)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_flip()  + 
  labs(x = "", y = "Average Length of Stay") +
  theme_classic() +
  theme(legend.position="NA")

ADF <- group %>%
  mutate(Park = fct_reorder(Park, avgdateDiff)) %>%
  ggplot(aes(y = avgdateDiff, x = Park)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_flip()  + 
  labs(x = "", y = "Average Booking Horizon") +
  theme_classic() +
  theme(legend.position="NA")

jpeg("Park_descriptive.jpeg")
grid.arrange(ANP, OCC, AVF, ALS, ADF, ncol = 3)
dev.off()
```

```{r summary excel file}
summary <- describeBy(descriptive, group = descriptive$Park, digits = 2)
summary <- do.call("rbind", summary)
fwrite(summary, file = "summary.csv", row.names = TRUE)

summary <- fread("summary.csv") 
summary <- separate(summary, c())

fwrite(summary, file = "summary2.csv", row.names = TRUE)

summary <- fread("summary2.csv")
summary <- data.frame(left_join(summary, parklist, by=c("V1"="Campground")))
#rename column Park to Campground and Park.y to Park
colnames(summary)[colnames(summary)=="Park"] <- "park"
colnames(summary)[colnames(summary)=="V1"] <- "campground"
colnames(summary)[colnames(summary)=="V2"] <- "variable"
summary <- transform(summary,id=as.numeric(factor(summary$campground)))
list <- unique(summary$id) #108 id's created

summary_long <- select(summary, id, campground, park, variable, numOfSites, mean, median, min, max)
summary_long <- summary_long[summary_long$variable!="HistoricalReservationID" & summary_long$variable!="ParentLocation*" & summary_long$variable!="ProductID" & summary_long$variable!="campground*" & summary_long$variable!="StartDate*" & summary_long$variable!="EndDate*" & summary_long$variable!="OrderDate*" & summary_long$variable!="date*" & summary_long$variable!="Park*" & summary_long$variable!="Notes*" & summary_long$variable!="numOfSites" & summary_long$variable!="RegionDescription*" & summary_long$variable!="minDate*" & summary_long$variable!="maxDate*",]
fwrite(summary_long, file="summary_long.csv", row.names = T)

#summary_wide <- dcast(summary_long, park+id ~ variable, value.var="mean")
summary_wide <- reshape(summary_long, idvar = c("id", "campground", "park", "numOfSites"), direction = "wide", timevar = "variable", sep = "_")
summary_wide$numOfSites <- as.numeric(summary_wide$numOfSites)
summary_wide$park[is.na(summary_wide$park)] <- "Lassen Volcanic" 
summary_wide$numOfSites[summary_wide$campground=="BUTTE LAKE STOCK CORRAL"] = 1 ##BUTTE LAKE STOCK CORRAL was missing its park and capacity info (https://www.nps.gov/lavo/planyourvisit/butte-lake-stock.htm)
summary_wide$park[summary_wide$park=="Lassen Volanic"] <- "Lassen Volcanic" ##there was typo...
summary_wide$park[summary_wide$campground=="Grey Cliffs Campground"] <- "Great Basin" ##Grey Cliffs Campground is in Great Basin
fwrite(summary_wide, "summary_wide.csv")
```

As the reservation data only has occupancy information for the dates that were occupied, we do not have data for the dates where there were no reported reservations/occupanices (it could be off-season too). Hence, there are gaps in the dates. We need to fill in those gaps so that our time series do not just jump over. Create the missing dates and fill in 0's as occupancy. 

```{r fill in missing dates}
rm(initialData) #clear some space
test_data <- data %>%
  select(id, Park, Campground, date, occupancy, avglengthStay, avgfee, avgdateDiff, totalNumberOfPeople, avgNumberOfPeople, aggPaid, avgPaid, numOfSites, recGovNumOfSites)

newData <- NULL
#For each ID, create the sequence of dates and fill in with either 0 (occupancy, fee, cost) or existing value (names and ID's)
list <- unique(data$id)

for (i in list) {
  temp <- test_data[test_data$id==i,]
  temp$date <- as.Date(temp$date, format="%Y-%m-%d")
  start = min(as.Date(temp$date, format="%Y-%m-%d"))
  end = max(as.Date(temp$date, format="%Y-%m-%d"))
  temp <- temp %>%
    complete(date = seq.Date(start, end, by="day")) %>% 
    distinct(date, .keep_all = TRUE)
  temp <-temp %>%
    mutate(id = na.locf(i, na.rm=FALSE)) %>%
    mutate(Campground = na.locf(Campground, na.rm=FALSE)) %>% 
    mutate(Park = na.locf(Park, na.rm=FALSE)) %>% 
    mutate(occupancy = replace_na(occupancy, 0)) %>%
    mutate(avgfee = replace_na(avgfee, 0)) %>%
    mutate(aggPaid = replace_na(aggPaid, 0)) %>%
    mutate(avgPaid = replace_na(avgPaid, 0)) %>%
    mutate(avgNumberOfPeople = replace_na(avgNumberOfPeople, 0)) %>%
    mutate(totalNumberOfPeople = replace_na(totalNumberOfPeople, 0)) %>%
    mutate(avgdateDiff = replace_na(avgdateDiff, 0)) %>%
    mutate(avglengthStay = replace_na(avglengthStay, 0)) %>%
    mutate(numOfSites = na.locf(numOfSites, na.rm=FALSE)) %>% 
    mutate(recGovNumOfSites = na.locf(recGovNumOfSites, na.rm=FALSE))
  newData <- bind_rows(newData, temp)
}

rm(temp)

fwrite(newData, "time_series3.csv")
```

```{r graphs}
#Average Use Fee vs. Average Number of People
jpeg('ADF_vs_ANP.jpg')
p1 <- ggplot(summary_wide, aes(x=mean_avgNumberOfPeople, y=mean_perDayFee)) +geom_point(aes(color=park))+ 
  labs(x="Average Number of People", y="Average Use Fee") + theme(legend.position="bottom", legend.key.size = unit(0.02, "cm"), legend.title=element_blank())
dev.off()

jpeg('ADF_vs_ALS.jpg')
p2 <- ggplot(summary_wide, aes(x=mean_avglengthStay, y=mean_perDayFee)) +geom_point(aes(color=park))+ 
  labs(x="Average Length of Stay", y="Average Use Fee") + theme(legend.position="bottom", legend.key.size = unit(0.02, "cm"), legend.title=element_blank())
dev.off()

jpeg('ADF_vs_ANP_ALS.jpg')
grid_arrange_shared_legend(p1, p2, ncol=2, nrow=1)
dev.off()

#lengthStay vs. dateDiff
jpeg('ALS_vs_ARG.jpg')
p3 <- ggplot(summary_wide, aes(x=mean_avglengthStay, y=mean_avgdateDiff)) + geom_point(aes(color=park)) + 
  labs(x="Average Length of Stay", y="Average Horizon") + theme(legend.position="bottom", legend.key.size = unit(0.02, "cm"), legend.title=element_blank())
dev.off()

jpeg('ALS_vs_MRG.jpg')
p4 <- ggplot(summary_wide, aes(x=mean_avglengthStay, y=median_avgdateDiff)) + geom_point(aes(color=park)) + 
  labs(x="Average Length of Stay", y="Median Horizon") + theme(legend.position="bottom", legend.key.size = unit(0.02, "cm"), legend.title=element_blank())
dev.off()

jpeg('ALS_vs_AMRG.jpg')
grid_arrange_shared_legend(p3, p4, ncol=2, nrow=1)
dev.off()

#occupancy

occupancy <- summary_wide %>%
  group_by(park) %>%
  mutate(mean_occupancy=mean(mean_occupancy/numOfSites)) %>%
  mutate(median_occupancy=mean(median_occupancy/numOfSites)) %>%
  mutate(mean_avgNumberOfPeople=mean(mean_avgNumberOfPeople)) %>%
  mutate(median_avgNumberOfPeople=mean(median_avgNumberOfPeople)) %>%
  mutate(mean_totalNumberOfPeople=mean(mean_totalNumberOfPeople)) %>%
  mutate(median_totalNumberOfPeople=mean(median_totalNumberOfPeople)) %>% select(campground, park, mean_avgNumberOfPeople, median_avgNumberOfPeople, mean_totalNumberOfPeople, median_totalNumberOfPeople, mean_occupancy, median_occupancy, numOfSites) %>%
  transform(id=as.numeric(factor(park)))

occupancy1 <- distinct(occupancy, id, park, mean_occupancy)
occupancy2 <- distinct(occupancy, id, park, median_occupancy)
occupancy3 <- distinct(occupancy, id, park, mean_avgNumberOfPeople)
occupancy4 <- distinct(occupancy, id, park, median_avgNumberOfPeople)
occupancy5 <- distinct(occupancy, id, park, mean_totalNumberOfPeople)
occupancy6 <- distinct(occupancy, id, park, median_totalNumberOfPeople)



jpeg('occupancy.jpg')
p5 <- ggplot(occupancy1, aes(x=id, y=mean_occupancy)) + 
  geom_bar(stat="identity", aes(fill=park)) + 
  geom_bar(data=occupancy2, aes(x=id, y=median_occupancy), linetype="dashed", color="dark grey", fill="NA", stat="identity") + 
  geom_text(aes(label = id), vjust = 1, size=3) + 
  labs(x="Park", y="Occupancy (%)")   + theme_bw() + 
  theme(axis.text.x = element_blank(), legend.position="none", legend.key.size = unit(0.02, "cm"), legend.title=element_blank())

p6 <- ggplot(occupancy3, aes(x=id, y=mean_avgNumberOfPeople)) + 
  geom_bar(stat="identity", aes(fill=park)) + 
  geom_bar(data=occupancy4, aes(x=id, y=median_avgNumberOfPeople), linetype="dashed", color="dark grey", fill="NA", stat="identity") + 
  geom_text(aes(label = id), vjust = 1, size=3) + 
  labs(x="Park", y="Average Number of People per Day")   + theme_bw() + 
  theme(axis.text.x = element_blank(), legend.position="none", legend.key.size = unit(0.02, "cm"), legend.title=element_blank())

p7 <- ggplot(occupancy5, aes(x=id, y=mean_totalNumberOfPeople)) + 
  geom_bar(stat="identity", aes(fill=park)) + 
  geom_bar(data=occupancy6, aes(x=id, y=median_totalNumberOfPeople), linetype="dashed", color="dark grey", fill="NA", stat="identity")  + 
  geom_text(aes(label = id), vjust = 1, size=3) + 
  labs(x="Park", y="Total Number of People")  + theme_bw() + 
  theme(legend.position="bottom", legend.key.size = unit(0.02, "cm"), legend.title=element_blank())

grid_arrange_shared_legend(p5, p6, p7, ncol=3, nrow=1)

dev.off()
```

```{r grid arrange function}
grid_arrange_shared_legend <- function(..., ncol = length(list(...)), nrow = 1, position = c("bottom", "right")) {
	plots <- list(...)
	position <- match.arg(position)
	g <- ggplotGrob(plots[[1]] + 
	theme(legend.position = position))$grobs
	legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
	lheight <- sum(legend$height)
	lwidth <- sum(legend$width)
	gl <- lapply(plots, function(x) x +
	theme(legend.position = "none"))
	gl <- c(gl, ncol = ncol, nrow = nrow)

	combined <- switch(position,
	                   "bottom" = arrangeGrob(do.call(arrangeGrob, gl), 
	                   legend,ncol = 1,
					heights = unit.c(unit(1, "npc") - lheight, lheight)),
					"right" = arrangeGrob(do.call(arrangeGrob, gl),
				  legend, ncol = 2,
					widths = unit.c(unit(1, "npc") - lwidth, lwidth)))

	grid.newpage()
	grid.draw(combined)

	# return gtable invisibly
	invisible(combined)
}
```

